---
title: "Analysis"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
```

```{r}
library(dplyr)
library(MASS)
library(ROCR)

readmit2 <- read.csv("~/Documents/Multivariable\ Analysis/final_project/archive/readmit2.csv", header = TRUE, stringsAsFactors = TRUE)

readmit2$admission_source_id <- as.factor(readmit2$admission_source_id)
readmit2$admission_type_id <- as.factor(readmit2$admission_type_id)
readmit2$discharge_disposition_id <- as.factor(readmit2$discharge_disposition_id)

attach(readmit2)
```
Missing data was removed for the variables of interest. The following variables were missing too much data to justify including them in the full model: max glucose serum, A1C result, and weight.

```{r, echo=FALSE}
readmit3 <- readmit2 %>% 
  filter(!is.na(insulin2),
         !is.na(diabetesMed2),
         !is.na(age2),
         !is.na(number_inpatient),
         !is.na(time_in_hospital),
         !is.na(number_emergency),
         !is.na(number_diagnoses),
         !is.na(discharge_disposition_id))
```

Descriptives
Readmitted within 30 days
```{r}
transform(table(readmit3$readmitted30), Percent = 100*prop.table(Freq), cumFreq = cumsum(Freq))
```
Age
```{r}
summary(readmit3$age2)
```

Sex
```{r}
transform(table(readmit3$gender2), Percent = 100*prop.table(Freq), cumFreq = cumsum(Freq))
```
A1C
```{r}
transform(table(readmit3$A1Cresult2), Percent = 100*prop.table(Freq), cumFreq = cumsum(Freq))
```
Glucose serum
```{r}
transform(table(readmit3$max_glu_serum2), Percent = 100*prop.table(Freq), cumFreq = cumsum(Freq))
```
Time in hospital
```{r}
summary(readmit3$time_in_hospital)
```

Full model
```{r, echo=FALSE}
readmit3.logit_full <- glm(data = readmit3, readmitted30 ~ number_inpatient +  number_emergency + discharge_disposition_id + num_medications + admission_type_id + number_diagnoses + metformin + glipizide + insulin2, family = "binomial")
summary(readmit3.logit_full)
# Odds Ratio
#exp(cbind(OR = coef(readmit3.logit_full),
#          confint(readmit3.logit_full)))
```

Forward selection
```{r, echo=FALSE}
# Forward Selection

readmit3.logit_intercept <- glm(data = readmit3, readmitted30 ~ 1, family = "binomial")
readmit3.logit_forward <- stepAIC(readmit3.logit_intercept, direction = "forward", scope = formula(readmit3.logit_full), trace = FALSE)
readmit3.logit_forward$anova
```

Backward elimination
```{r, echo=FALSE}
# Backward Elimination
readmit3.logit_backward <- stepAIC(readmit3.logit_full, direction = "backward", scope = formula(readmit3.logit_full), trace = FALSE)
readmit3.logit_backward$anova
```

Final model (race eliminated)
```{r, echo=FALSE}
# Final Model
readmit3.logit_final <- glm(data = readmit3, readmitted30 ~ number_inpatient + discharge_disposition_id + num_medications + number_diagnoses + metformin + insulin2, family = "binomial")
summary(readmit3.logit_final)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_final),
          confint(readmit3.logit_final)))
```

ROC analysis
```{r, echo=FALSE}
# ROC Analysis
prob = predict(readmit3.logit_final, type = "response")
ROCRpred <- prediction(prob, readmit3$readmitted30)

ROCRperf <- performance(ROCRpred, measure = "auc")
print(ROCRperf@y.values)

ROCRperf <- performance(ROCRpred, measure = "tpr", x.measure = "fpr")
plot(ROCRperf, lwd = 2, xlab="1-Specificity", ylab="Sensitivity")
abline(0, 1, lwd = 2, lty = 2) #add a 45 degree dashed line
```

Numbers
```{r, echo=FALSE}
sum(readmit3$discharge_disposition_id==1)
sum(readmit3$discharge_disposition_id==2)
sum(readmit3$discharge_disposition_id==3)
sum(readmit3$discharge_disposition_id==4)
sum(readmit3$discharge_disposition_id==6)
sum(readmit3$discharge_disposition_id==7)
sum(readmit3$discharge_disposition_id==8)
sum(readmit3$discharge_disposition_id==13)
sum(readmit3$discharge_disposition_id==14)
sum(readmit3$discharge_disposition_id==15)
sum(readmit3$discharge_disposition_id==22)
sum(readmit3$discharge_disposition_id==23)
sum(readmit3$discharge_disposition_id==24)
sum(readmit3$discharge_disposition_id==28)
sum(readmit3$metformin=="Down")
sum(readmit3$metformin=="Up")
sum(readmit3$metformin=="Steady")
sum(readmit3$metformin=="No")
sum(readmit3$insulin2=="Down")
sum(readmit3$insulin2=="Up")
sum(readmit3$insulin2=="Steady")
sum(readmit3$insulin2=="No")
sum(!is.na(num_medications))
sum(!is.na(number_diagnoses))
sum(!is.na(number_inpatient))
```