---
title: "exploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
```

```{r summary, echo=FALSE}
readmit2 <- read.csv("~/Documents/Multivariable\ Analysis/final_project/archive/readmit2.csv", header = TRUE, stringsAsFactors = TRUE)

attach(readmit2)

summary(readmit2)
```

Race
```{r race, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$race2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$race2), margin = 2),  digits = 1),  margin = 1))
```
Gender
```{r gender, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$gender2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$gender2), margin = 2),  digits = 1),  margin = 1))
```
Max Glu Serum
```{r glu, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$max_glu_serum2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$max_glu_serum2), margin = 2),  digits = 1),  margin = 1))
```
A1C
```{r a1c, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$A1Cresult2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$A1Cresult2), margin = 2),  digits = 1),  margin = 1))
```
Insulin
```{r insulin, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$insulin2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$insulin2), margin = 2),  digits = 1),  margin = 1))
```
Change
```{r change, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$change2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$change2), margin = 2),  digits = 1),  margin = 1))
```
DiabetesMed
```{r diabetesmed, echo=FALSE}
cbind(addmargins(table(readmit2$readmitted30, readmit2$diabetesMed2), margin = 1),
      addmargins(round(100*prop.table(table(readmit2$readmitted30, readmit2$diabetesMed2), margin = 2),  digits = 1),  margin = 1))
```
Age
```{r age, echo=FALSE}
boxplot(age2~readmitted30,data=readmit2)
```
Weight
```{r weight, echo=FALSE}
boxplot(weight2~readmitted30,data=readmit2)
```
Time in hospital
```{r hosptime, echo=FALSE}
boxplot(time_in_hospital~readmitted30,data=readmit2)
```
Num lab procedures
```{r lab, echo=FALSE}
boxplot(num_lab_procedures~readmitted30,data=readmit2)
```
Num procedures
```{r procedures, echo=FALSE}
boxplot(num_procedures~readmitted30,data=readmit2)
```
Num medications
```{r medications, echo=FALSE}
boxplot(num_medications~readmitted30,data=readmit2)
```
Num outpatient
```{r outpatient, echo=FALSE}
boxplot(number_outpatient~readmitted30,data=readmit2)
```
Num emergency
```{r emergency, echo=FALSE}
boxplot(number_emergency~readmitted30,data=readmit2)
```
Num inpatient
```{r inpatient, echo=FALSE}
boxplot(number_inpatient~readmitted30,data=readmit2)
```
Num diagnoses
```{r diagnoses, echo=FALSE}
boxplot(number_diagnoses~readmitted30,data=readmit2)
```
Unadjusted model - race
```{r unadj_race, echo=FALSE}
readmit2.logit_race <- glm(data = readmit2, readmitted30 ~ race2, family = "binomial")
summary(readmit2.logit_race)
```
Unadjusted model - max glu serum
```{r unadj_glu, echo=FALSE}
readmit2.logit_glu <- glm(data = readmit2, readmitted30 ~ max_glu_serum2, family = "binomial")
summary(readmit2.logit_glu)
```
Unadjusted model - A1C
```{r unadj_a1c, echo=FALSE}
readmit2.logit_a1c <- glm(data = readmit2, readmitted30 ~ A1Cresult2, family = "binomial")
summary(readmit2.logit_a1c)
```
Unadjusted model - Insulin
```{r unadj_ins, echo=FALSE}
readmit3.logit_ins <- glm(data = readmit3, readmitted30 ~ insulin2, family = "binomial")
summary(readmit3.logit_ins)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_ins),
          confint(readmit3.logit_ins)))
```
Unadjusted model - Metformin
```{r unadj_ins, echo=FALSE}
readmit3.logit_met <- glm(data = readmit3, readmitted30 ~ metformin, family = "binomial")
summary(readmit3.logit_met)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_met),
          confint(readmit3.logit_met)))
```

Unadjusted model - Change
```{r unadj_ch, echo=FALSE}
readmit2.logit_ch <- glm(data = readmit2, readmitted30 ~ change2, family = "binomial")
summary(readmit2.logit_ch)
```
Unadjusted model - DiabetesMed
```{r unadj_dM, echo=FALSE}
readmit2.logit_dM <- glm(data = readmit2, readmitted30 ~ diabetesMed2, family = "binomial")
summary(readmit2.logit_dM)
```
Unadjusted model - Weight
```{r unadj_wt, echo=FALSE}
readmit2.logit_wt <- glm(data = readmit2, readmitted30 ~ weight2, family = "binomial")
summary(readmit2.logit_wt)
```
Unadjusted model - Age
```{r unadj_age, echo=FALSE}
readmit2.logit_age <- glm(data = readmit2, readmitted30 ~ age2, family = "binomial")
summary(readmit2.logit_age)
```
Unadjusted model - Number inpatient
```{r unadj_inp, echo=FALSE}
readmit3.logit_inp <- glm(data = readmit3, readmitted30 ~ number_inpatient, family = "binomial")
summary(readmit3.logit_inp)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_inp),
          confint(readmit3.logit_inp)))
```
Unadjusted model - Number diagnoses
```{r unadj_dx, echo=FALSE}
readmit3.logit_dx <- glm(data = readmit3, readmitted30 ~ number_diagnoses, family = "binomial")
summary(readmit3.logit_dx)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_dx),
          confint(readmit3.logit_dx)))
```
Unadjusted model - Number medications
```{r unadj_dx, echo=FALSE}
readmit3.logit_med <- glm(data = readmit3, readmitted30 ~ num_medications, family = "binomial")
summary(readmit3.logit_med)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_med),
          confint(readmit3.logit_med)))
```
Unadjusted model - Discharge location
```{r unadj_ins, echo=FALSE}
readmit3.logit_dis <- glm(data = readmit3, readmitted30 ~ discharge_disposition_id, family = "binomial")
summary(readmit3.logit_dis)
# Odds Ratio
exp(cbind(OR = coef(readmit3.logit_dis),
          confint(readmit3.logit_dis)))
```

Based on this exploration, the following variables were chosen to be of interest, due to either being a significant predictor of readmission within 30 days or a conceptual likelihood that they would be important:

Race
Max Glu Serum
A1C
Insulin *
Change *
DiabetesMed *
Weight
Age *
Number inpatient *
Number diagnoses *